### 2019-01-05 Sections/optimising_the_world.tex
Quotes, editing
minor

@@

This joke is of course based on the assumption that quantum computers can efficiently and optimally solve the chess problem, foreseeing the entire future of a game, and determining the perfect optimal next move. Thus, after making the optimal first move `e3', black concedes that he cannot win.

@@

Some problems in even harder classes than \textbf{NP}-complete can in some instances be \textit{approximated} using the same approach. The key to solving such problems is to define an oracle\index{Oracles} that attributes a \textit{score}\index{Score} to a given input, rather than a yes/no answer to perfect satisfiability, and answers `yes' or `no' depending on whether that score is above some defined threshold for approximation. As an illustrative example, consider the optimisation of, say, a complex traffic network, where the goal is to maximise flow through the network. Then we might define our score to be some flow metric for the network's graph.

@@

How do current classical computers play chess? They construct a \textit{search tree}\index{Search tree} (see Fig.~\ref{fig:search_tree}), which is explored exhaustively up to a given depth (bounded by computational resources), and assign a score to each board position, indicating the relative strength of its position. The branch in the tree with the highest scores determines the next move.

>>>>

\famousquote{Premature optimisation is the root of all evil.}{Donald Knuth}
\newline

@@

This joke is of course based on the assumption that quantum computers can efficiently and optimally solve the chess problem, foreseeing the entire future of a game, and determine the perfect optimal next move. Thus, after making the optimal first move `e3', black concedes that he cannot win.

@@

Some problems in even harder classes than \textbf{NP}-complete can in some instances be \textit{approximated} using the same approach as for \textbf{NP}-complete problems. The key to solving such problems is to define an oracle\index{Oracles} that attributes a \textit{score}\index{Score} to a given input, rather than a yes/no answer to perfect satisfiability, and answers `yes' or `no' depending on whether that score is above some defined threshold for approximation. As an illustrative example, consider the optimisation of, say, a complex traffic network, where the goal is to maximise flow through the network. Then we might define our score to be some flow metric for the network's graph.

@@

How do current classical computers play chess? They construct a \textit{search tree}\index{Search tree} (see Fig.~\ref{fig:search_tree}), which is explored exhaustively up to a given depth (bounded by computational resources), and assign a score to each board position, indicating its relative strength. The branch in the tree with the highest scores determines the next move.
